Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-02 Paper.tex
Add RLP R_b and R_l word defs.

If the value to be serialised is a byte-array, the RLP serialisation takes one of three forms:

@@

If instead, the value to be serialised is a sequence of other items then the RLP serialisation takes one of two forms:

>>>>

\hypertarget{RLP_serialisation_of_a_byte_array_R__b_word_def}{}If the value to be serialised is a byte-array, the RLP serialisation takes one of three forms:

@@

\hypertarget{RLP_serialisation_of_a_sequence_of_other_items_R__l_word_def}{}If instead, the value to be serialised is a sequence of other items then the RLP serialisation takes one of two forms:
